An R Markdown document converted from "03_ValClusOutcomes.ipynb

### 2023-09-20 03_ValClusOutcomes.Rmd
Add files via upload

These two tables include individuals followed ***up to 10 years***. This means that any outcome after 10 years is censored. `outcome_value` is 1 if the person experienced the event during the follow-up time and 0 if not. `outcome_timeyrs` is the time of follow-up in years, up to the first event or up to 10 years.

@@

@@

We will also calculate overall and cluster-specific cumulative incidence rates using the Kaplan-Meier method:

```{r}
kmestdf <- kmestfx(clustersurvdfs)
```

```{r}
head(kmestdf)
```

@@

```{r}
result_file2 <- list(
    MarkerDistrib = markerdistribdf,
    BMIeffOnMarker = bmieffmarkerdf,
    CountCovars = countcovarsdf,
    CountDXMeds = countdxmed,
    CrossSectAssoc = assocdxdf,
    RatesByClus = ratesbyclus,
    RatesByClusMeds = ratesbyclusmed,
    KaplanMeierDF = kmestdf,
    SurvCoefs = survcoefs,
    Comparison = compmoddf,
    AdeqIndByClus = adeqindbyclus,
    AdeqIndByPre = adeqindbypre,
    DCARes = dcares,
    DCAClusREs = dcaclusres,
    InteractMods = interactmods
)
```

>>>>

These two tables should include individuals followed ***up to 10 years***. Any outcome after 10 years should be censored. `outcome_value` is 1 if the person experienced the event during the follow-up time and 0 if not. `outcome_timeyrs` is the time of follow-up in years, up to the first event or up to 10 years.

@@

## Creating follow-up subsets

In each subset the follow-up will be censored at a specific point in time:

```{r}
clustersurvdfs <- futsubsetsfx(clustersurvdfs)
print(clustersurvdfs)
```

## Summary of survival data

We need information on the data available for survival analysis. Here is the function:

```{r}
survsum <- survsumfx(clustersurvdfs)
survsum
```

@@

@@

```{r}
result_file2 <- list(
    MarkerDistrib = markerdistribdf,
    BMIeffOnMarker = bmieffmarkerdf,
    CountCovars = countcovarsdf,
    CountDXMeds = countdxmed,
    CrossSectAssoc = assocdxdf,
    SurvSum = survsum,
    RatesByClus = ratesbyclus,
    RatesByClusMeds = ratesbyclusmed,
    SurvCoefs = survcoefs,
    Comparison = compmoddf,
    AdeqIndByClus = adeqindbyclus,
    AdeqIndByPre = adeqindbypre,
    DCARes = dcares,
    DCAClusREs = dcaclusres,
    InteractMods = interactmods
)
```
